Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-06 robdml.tex
tex
u

Then, we want change (increase) the hardness level from $H_S$ into $H_D$, by
finding adversarial examples for $(X_a, X_p^S, X_n^S)$.
%
Note, it is not expected to lower the hardness during the attack, namely
$E[H_D]$ should be greater or equal to $E[H_S]$.
%
We denote the the hardness of adversarial examples as $\tilde{H}_S=H(X_a{+}r_a,
X_p^S{+}r_p, X_n^S{+}r_n)$.
%
This is named as \emph{Hardness Manipulation} (HM), which is implemented as
follows:
%
\begin{equation}
	%
	\bar{r}_a, \bar{r}_p, \bar{r}_n =
	\argmin_{r_a,r_p,r_n} \|\min(0, \tilde{H}_S-H_D)\|^2.
	%
	\label{eq:hm}
	%
\end{equation}
%
The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_S>H_D$,
preventing $H_S$ from being reduced.
%
The optimization problem can be solved by projected gradient
descent~\cite{madry}.
%
And the resulting adversarial examples are used for adversarially training
the DML model:
%
$L_\text{trip}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
\phi(X_n^S+\bar{r}_n))$.

@@

>>>>

Then, we want change (increase) the hardness level from $H_S$ into $H_D$, by
finding adversarial examples for $(X_a, X_p^S, X_n^S)$.
%
Note, it is not expected to lower the hardness during the attack, namely
$E[H_D]$ should be greater or equal to $E[H_S]$.
%
We denote the the hardness of adversarial examples as $\tilde{H}_S=H(X_a{+}r_a,
X_p^S{+}r_p, X_n^S{+}r_n)$.
%
This is named as \emph{Hardness Manipulation} (HM), which is implemented as
follows:
%
\begin{equation}
	%
	\bar{r}_a, \bar{r}_p, \bar{r}_n = \argmin_{r_a,r_p,r_n} \|\min(0,
	\tilde{H}_S-H_D)\|^2.
	%
	\label{eq:hm}
	%
\end{equation}
%
The $\min(0,\cdot)$ part in \cref{eq:hm} truncates the gradient when $H_S>H_D$,
automatically stopping the optimization.
%
This is because $H_S$ will be reduced once greater than $H_D$ in standard Mean
Square Error.
%
The optimization problem can be solved by projected gradient
descent~\cite{madry}.
%
And the resulting adversarial examples are used for adversarially training the
DML model:
%
$L_\text{trip}(\phi(X_a+\bar{r}_a), \phi(X_p^S+\bar{r}_p),
\phi(X_n^S+\bar{r}_n))$.

@@

During the training process, the strength of adversary will gradually decrease,
because the expectation of the destination hardness $E[H_D]$ is expected to
decrease with a model being trained.

\[
	\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times
	(U_H + (H_D - H_S).relu())
\]
